---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here:



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE

ideo <- recode(cces$ideo5, '1' = "Very Liberal", '2' = "Liberal", '3' = "Moderate", '4' = "Conservative", '5' = "Very Conservative")
cces<-add_column(cces,ideo)
ggplot (cces, aes(x=ideo, fill=ideo))+
  geom_bar()+
  guides(fill=FALSE)+
  labs(x="Ideology", y = "Count", title = "Respondent Ideology")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE

pew_religion <- recode (cces$pew_religimp, '1' = "Very Important", '2' = "Somewhat Important", '3' = "Not too Important", '4' = "Not at all Important")
Ideology <- recode(cces$ideo5, '1' = "Very Liberal", '2' = "Liberal", '3' = "Moderate", '4' = "Conservative", '5' = "Very Conservative")
ggplot (cces, aes(x=pew_religion, fill=Ideology))+
  geom_bar()+
  labs(x="Importance of Religion", y = "Count", title = "Importance of Religion by Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE

Semester <- c(1,2,3,4,5,6,1,2,3,4,5,6,1,2,3,4,5,6)
Student <- c("Amanda", "Amanda","Amanda","Amanda","Amanda","Amanda","Betty","Betty","Betty","Betty","Betty","Betty", "Carol","Carol","Carol","Carol","Carol","Carol")
Grade<-runif(18, min=80, max=100)
df<-tibble("Student" = Student, "Semester"=Semester, "Grade"=Grade)
ggplot(df, (aes(x=Semester,y=Grade, group=Student, colour=Student)))+
  labs(title = "Students grade by Semester")+
  geom_line()+
  theme(legend.position = "None")+
  facet_wrap(~Student)

```
